Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-06 manuscript/manuscript.tex
included new figs

>>>>

\vb{Additionally, we looked at the effect the size of each replicate population
  has on a single population's $G(t)$ trajectories. These simulations had the
  same $10N$ generation burnin, followed by a change in population size
  emulating the bottlenecks associated with creating selection lines. Overall,
  we find that smaller population sizes lead to a reduced $G(t)$ (Supplementary
  Material Figure \ref{suppfig:gss-G-sampleN}). This is expected, as the
  denominator of $G(t)$ is $\var(p_t - p_0)$, which has an inverse relationship
with $N_e$; as replicate population size is reduced, the proportion of allele
frequency change driven by linked selection is lower, since the rate of drift
is increased.}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/gss-G-sampleN.pdf}

  \caption{$G(t)$ trajectories for a sudden optima shift of 1, for varying
  replicate population sizes.}

  \label{suppfig:gss-G-sampleN}
\end{figure}
